Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-08-15 schemes.tex
more corrections
corrections and density regions estimate script

In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
in the $i$-th recoded packet and assigned to multiply a previously
coded packet $C_j$. These coding coefficients are again uniformly and
randomly chosen from $GF(q)$. However, these $w_{ij}$'s are not
appended to the previous coding coefficients.  Instead, the system
will update the previous coefficients. Due to the linearity of the
operation, this update reduces to recombining the coding coefficients
equivalent to each original packet with the weight of the
$w_{i,j}$.Therefore, we define the local coding matrix $\textbf{W}$ in
the same way as it was made for $\textbf{V}$. Thus, the local coding
matrix can be written as:
%
\begin{align} \label{eq:local_coding_matrix}
\textbf{W} =
\left[
\begin{array}{c}
        w_1    \\ \hline
        \vdots \\ \hline
        w_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        w_{11} & \ldots & w_{1g} \\
        \vdots  & \ddots & \vdots  \\
        w_{g1} & \ldots & w_{gg} \\
\end{array}
\right].
\end{align}
%
With the definitions from \eqref{eq:coding_matrix} and
\eqref{eq:local_coding_matrix}, the recoded packets
$\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$. Here, we recognize
the relationship between original and recoded packets. The resulting
coding matrix is simply the multiplication of matrices $\textbf{W}$ and
$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
term is the resulting coding coefficient used to create $R_i$ after
encoding the original packet $P_j$ recoding it locally in an intermediate
node. Finally, the appended coefficients for $R_i$ are
${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,g]$. By doing some
algebra, each ${(\textbf{W} \textbf{V})}_{ij}$ term can be verified to be
computed as:
%
\begin{align}
\label{eq:appended_coded_coefficients}
{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g].
\end{align}
%
This update procedure on the coding coefficients is carried by all the
recoders in a given network therefore allowing any decoder to compute
the original data after Gaussian elimination, regardless of the amount
of times recoding was performed and without incurring in any
additional overhead cost for signaling. Similar to the encoding
operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
packets with their respective coefficients, will be able to decode the
data as mentioned before in Section \ref{sssec:decoding}.

@@

Provided a desired budget $b$ and the \ac{dof} of the decoder, an encoder
can estimate the required coding density for the packets to not exceed the
budget. In our implementation, we use feedback packets to provide the
encoder an estimate of the decoder \ac{dof} at pre-defined points of the
transmission process. The points in the process occur when a decoder
obtains a given amount of \ac{dof}. In our implementation, we define $r(k),\
k \in [1, \ldots)$ as the rank $r$ of the decoder\footnote{The rank of
a decoder is the rank of its coding matrix at a given point in the
transmissions process.} where a decoder has to send the $k$-th feedback in
\eqref{eq:feedback_dofs}.
%
\begin{equation}\label{eq:feedback_dofs}
    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in [1,\ldots)
\end{equation}
%
At the beginning of the transmission process, we assume that the encoder
starts with an initial coding density that has been calculated depending to
the budget. According to \eqref{eq:feedback_dofs}, a decoder sends feedback
once it has obtained (rounded down) $g/2,\ 3g/4,\ 7g/8,\ \ldots$  degrees of
freedom. The total amount of feedback for this scheme will depend on the
generation size. Still, we have an implementation that limits the amount of
feedback to be sent from the decoder in~\cite{practicalview_tsnc2015}.

>>>>

In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
in the $i$-th recoded packet and assigned to multiply a previously
coded packet $C_j$. These coding coefficients are again uniformly and
randomly chosen from $GF(q)$. However, these $w_{ij}$'s are not
appended to the previous coding coefficients.  Instead, the system
will update the previous coefficients. Due to the linearity of the
operation, this update reduces to recombining the coding coefficients
equivalent to each original packet with the weight of the
$w_{i,j}$.Therefore, we define the local coding matrix $\textbf{W}$ in
the same way as it was made for $\textbf{V}$. Thus, the local coding
matrix can be written as:
%
\begin{align} \label{eq:local_coding_matrix}
\textbf{W} =
\left[
\begin{array}{c}
        w_1    \\ \hline
        \vdots \\ \hline
        w_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        w_{11} & \ldots & w_{1g} \\
        \vdots  & \ddots & \vdots  \\
        w_{g1} & \ldots & w_{gg} \\
\end{array}
\right].
\end{align}
%
With the definitions from \eqref{eq:coding_matrix} and
\eqref{eq:local_coding_matrix}, the recoded packets
$\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$. Here, we recognize
the relationship between original and recoded packets. The resulting
coding matrix is the multiplication of matrices $\textbf{W}$ and
$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
term is the resulting coding coefficient used to create $R_i$ after
encoding the original packet $P_j$ recoding it locally in an intermediate
node. Finally, the appended coefficients for $R_i$ are
${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,g]$. By doing some
algebra, each ${(\textbf{W} \textbf{V})}_{ij}$ term can be verified to be
computed as:
%
\begin{align}
\label{eq:appended_coded_coefficients}
{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g].
\end{align}
%
This update procedure on the coding coefficients is carried by all the
recoders in a given network therefore allowing any decoder to compute
the original data after Gaussian elimination, regardless of the amount
of times recoding was performed and without incurring in any
additional overhead cost for signaling. Similar to the encoding
operation, any decoder that collects a set of $g$ \ac{l.i.} recoded
packets with their respective coefficients, will be able to decode the
data as mentioned before in Section \ref{sssec:decoding}.

@@

Provided a desired budget $b$ and the \ac{dof} of the decoder, an encoder
can estimate the required coding density for the packets to not exceed the
budget. In our implementation, we use feedback packets to provide the
encoder an estimate of the decoder \ac{dof} at pre-defined points of the
transmission process. The points in the process occur when a decoder
obtains a given amount of \ac{dof}. In our implementation, we define $r(k)$ as the \ac{dof}s of the decoder where it has to send the $k$-th feedback in
\eqref{eq:feedback_dofs}.
%
\begin{equation}\label{eq:feedback_dofs}
    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in \Big[1,\ldots,\ceil{log_2(g)}+1\Big]
\end{equation}
%
At the beginning of the transmission process, we assume that the encoder
starts with an initial coding density that has been calculated depending to
the budget. According to \eqref{eq:feedback_dofs}, a decoder sends feedback
once it has obtained (rounded down) $g/2,\ 3g/4,\ 7g/8,\ \ldots$  degrees of
freedom. The total amount of feedback for this scheme will depend on the
generation size. Still, we have an implementation that limits the amount of
feedback to be sent from the decoder in~\cite{practicalview_tsnc2015}.
